\Chapter{CONCLUSION}

Two beam acceleration (TBA) is a promising candidate for future high-energy machines. 
Active research and development on this topic is taking place at the AWA. 
There have already been successful demonstrations of single stage metallic and dielectric TBA at the AWA. 
Further, a simplified two stage scheme was also demonstrated, with both bunch trains passing through both decelerating structures. 
The last step is to demonstrate a fully staged TBA scheme, where each decelerating structure is driven by an independent bunch train.  
In order to achieve this, two beam lines are required, each with one decelerating structure.   
A kicker is used to route one bunch train into a second beam line. 
The work presented supports fully staged TBA by optimizing the design of the new beam line, 
including a determination of the adjustments needed to the kicker hardware.  
The beam line simulation and optimization were done using the \verb|OPAL| code on a high performance computing platform.  
Different optimization techniques were compared, and a solution for the beam line design was found that achieves 
100\% transmission of beam with good power generation through the decelerating structure. 

Initial experimental work included improving the ultraviolet~(UV) pulse train. 
This was done through careful measurement of the UV optics on the multisplitter table. 
Results showed the current splitters were of insufficient quality, and a higher grade set was ordered. 
Measurements of the new splitters took place to select the best combination for producing a uniform bunch train.
A considerable improvement in the UV pulse train intensity distribution was observed. 
The deviation between pulses was reduced by about 16.5\%.
Next RF power measurements were done for each of the accelerating cavities at the AWA. 
A pick up probe in the cavity sends a signal back to the control room when the accelerator is running. 
A power meter was used to measure the signal and the cables were calibrated to account for losses.  
These measurements helped guide simulation parameters. A solenoid scan was done using the data analysis script
and helped determine a source of discrepancy between experiment and simulations.

The beam properties must be determined for good understanding of beam generation and transport, 
as well as for comparison to simulation results. Several sets of energy measurements were taken. 
A dipole spectrometer was used for measuring beam energy. 
When the beam is bent by a known angle, the energy can be calculated. 
Probably the most important beam diagnostic at the AWA, 
because of their ease to use are the Yttrium Aluminum Garnet (YAG) screens. 
Cameras pointed at the YAG screens can take pictures of the 
transverse beam profile. 
Various data analysis techniques can then be used to determine 
the beam size and charge. A script was written in Python
to perform this analysis, and it is available on github for others to use. 
The last beam diagnostic used in this work was a Coherent Transition Radiation (CTR) screen. When the beam passes
through a specially designed foil in the beam line, 
it emits CTR. This light can be focused into a Michelson 
interferometer and used to calculate the bunch length. 
This is a difficult measurement due to the necessity of using a 
bolometer to measure intensity. 

The simulation work began with a benchmark between \verb|OPAL|, \verb|ASTRA|, and \verb|GPT| 
to confirm the correct use of \verb|OPAL|. 
Part of that work included convergence studies needed for computational parameters such as number of particles and grid size.
Bunch length simulations were compared to the experimental measurements. 
A model-based optimization method was used first, 
and compared to a genetic algorithm. 
Both methods returned similar results, indicating either
can be used for photoinjector optimization.  
Once \verb|OPAL| and the optimization techniques were well understood, 
the code was used to do the optimization of the new drive line for \SI{40}{nC} bunches.  
Particular attention was paid to the transverse beam size and bunch length at the entrance of the decelerating structure.  
This structure is the smallest aperture in the beam line. 
The bunch length affects the magnitude of power generation achievable in the structure.  
There is a trade-off in achieving small transverse emittance and short bunch length.  
The optimization produced a Pareto front whereby that trade-off could be understood, and the minimum combinations determined.

A fast rise time kicker design was modified and then fabricated and tested at the AWA. 
The kicker meets specifications and the deflection angle 
along with mechanical constraints were used to layout 
a fully staged TBA beam line. 
Massively parallel optimizations were then done to 
determine an optics configuration that would guarantee 
100\% transmission at the PETS location. 
A 2D solution was found that did not require use of the
last quadrupole focusing triplet in the beam  line. 
Differences in the 2D and 3D simulations indicate the optics 
solution needed to be adjusted to account for coherent synchrotron radiation (CSR) and 3D field maps. 
Since the 2D solution did not require hard focusing in any of the magnets, 
there was plenty of range to optimize the optics for the 3D scenario.
In conclusion, a beam line design was achieved that is capable of 
demonstrating fully staged TBA. 










